---
title: "R_Week_3_Hmk_607_Daniel_Thonn"
output: html_document
course: R-607 CUNY MSDA program

---

## Assignment Homework-3-607: Character manipulation and expressions

Summary of Assignment
This assignment involves character manipulation and expressions using R.

This Assignment requires the following:

1). R-Studio

The following R-packages are used:
1.stringr

Steps to reproduce:
1). run the R-Studio file: R_607_Week_3b_Hmk_Char_Manipulation_Daniel_Thonn.Rmd



Setting up and Preparing the Environment

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, echo=TRUE}

#install.packages("stringr")
library(stringr)
```


Load the character names data into an R dataframe


```{r, echo=TRUE}

name <- c("Moe Szyslak","Burns, C. Montgomery","Rev. Timothy Lovejoy","Ned Flanders", "Simpson, Homer","Dr. Julius Hibbert")
list(name)

```



3. Copy the introductory example. The vector name stores the extracted names.
R> name
[1] "Moe Szyslak" "Burns, C. Montgomery" "Rev. Timothy Lovejoy"
[4] "Ned Flanders" "Simpson, Homer" "Dr. Julius Hibbert"
(a) Use the tools of this chapter to rearrange the vector so that all elements conform to
the standard first_name last_name.
(b) Construct a logical vector indicating whether a character has a title (i.e., Rev. and
Dr.).
(c) Construct a logical vector indicating whether a character has a second name.


```{r, echo=TRUE}
#3a).

# use str_split: Split the elements of a character vector x into substrings according to the matches to substring split within them. 

# use sapply: traverse over a set of data like a list or vector, and calling the specified function for each item.

name2 = sapply(strsplit(name, split=", "),function(y) 
  {paste(rev(y),collapse=" ")})

list(name2)

#3b). Check Titles

#str_detect: .	str_detect() detects the presence or absence of a pattern and returns a logical vector 

has_title <- data.frame (name2, str_detect(name2,"Rev.|Dr."))
list (has_title)

#3c). Check Second Names

second_name <- data.frame(name, str_detect(name," [A-Z]\\."))
list (second_name)


```

4. Describe the types of strings that conform to the following regular expressions and
construct an example that is matched by the regular expression.
(a) [0-9]+\\$
(b) \\b[a-z]{1,4}\\b
(c) .*?\\.txt$
(d) \\d{2}/\\d{2}/\\d{4}
(e) <(.+?)>.+?</\\1>


```{r, echo=TRUE}
#4a).[0-9]+\\$ : contains one or more numbers then a $ sign

Four_a <- "111$"
str_detect(Four_a,"[0-9]+\\$")

#4b).\\b[a-z]{1,4}\\b: A word with one to four letters  

Four_b <- c("t","test","test1","testtt")
str_detect(Four_b,"\\b[a-z]{1,4}\\b")

#4c). .*?\\.txt$: A word with period and ending in .txt
Four_c <- c("test.txt","test","t.text","testtt.txt","txttxt")
str_detect(Four_c,".*?\\.txt$")

#4d). \\d{2}/\\d{2}/\\d{4} : character patterns with 2 digits, forward slash, 2 digits, forward slash, 4 digits

Four_d <- c("11/11/1111","1/11/1111","11/1/1111","11/11/111")
str_detect(Four_d,"\\d{2}/\\d{2}/\\d{4}")


```

9. The following code hides a secret message. Crack it with R and regular expressions.
Hint: Some of the characters are more revealing than others! The code snippet is also
available in the materials at www.r-datacollection.com.

clcopCow1zmstc0d87wnkig7OvdicpNuggvhryn92Gjuwczi8hqrfpRxs5Aj5dwpn0Tanwo
Uwisdij7Lj8kpf03AT5Idr3coc0bt7yczjatOaootj55t3Nj3ne6c4Sfek.r1w1YwwojigO
d6vrfUrbz2.2bkAnbhzgv4R9i05zEcrop.wAgnb.SqoU65fPa1otfb7wEm24k6t3sR9zqe5
fy89n6Nd5t9kc4fE905gmc4Rgxo5nhDk!gr


```{r, echo=TRUE}

string1 <- "clcopCow1zmstc0d87wnkig7OvdicpNuggvhryn92Gjuwczi8hqrfpRxs5Aj5dwpn0Tanwo
Uwisdij7Lj8kpf03AT5Idr3coc0bt7yczjatOaootj55t3Nj3ne6c4Sfek.r1w1YwwojigO
d6vrfUrbz2.2bkAnbhzgv4R9i05zEcrop.wAgnb.SqoU65fPa1otfb7wEm24k6t3sR9zqe5
fy89n6Nd5t9kc4fE905gmc4Rgxo5nhDk!gr"

string2 <-unlist(str_extract_all(string1,"[[:upper:].]{1,}"))
string2

string3 <- str_replace_all(paste(string2, collapse = ''), "[.]", " ")
string3


```
#END
